Multiset-trie data structure

### 2023-02-21 tex/tex/s_math-Theorems.tex
a lot of changes and added text to responses.

We find that the performance of the functions \textsc{submsetExistence} and 
\textsc{supermsetExistence} in the worst-case scenario is also exponential and 
does not depend on the outcome of the functions. We give a quite precise upper 
bound for the worst-case running time complexity, which appears to be the same 
for both functions. However, it must be stressed that for the positive outcome, an 
exponential behavior holds only on specific cases, such as the presence of the empty set 
in the multiset-trie.

>>>>

We find that the performance of the functions \textsc{submsetExistence} and 
\textsc{supermsetExistence} in the worst-case scenario is also proportional to the size of the constructed trie. We give a rather technical upper 
bound for the worst-case running time complexity, which appears to be the same 
for both functions. 
However, it must be stressed that for the positive outcome, this 
worst-case behavior holds only on specific cases, such as the presence of the empty set 
in the multiset-trie.
